\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-11-12 Manuscript/Manuscript.tex
added more to results section

papers 2, 5

@@

4, 10. The paper from \citet{3Teixeira2020} uses Multiple Level Logistic Regression to analyze the impact of cycling in various cities with different cycling infrastructure on stress markers. This analysis resulted in the data shown in Table ~\ref{fig:stress}.
\begin{figure}[tbp]
    \centering
    \includegraphics[width=0.5\textwidth]{stresstable2.jpeg}
    \caption{Distribution of Stress by City from Teixeira Study}
    \label{fig:stress}
\end{figure}

Two types of models were used in \citet{4Buehler2011}, a log-log Ordinary Least Square (OLS) model "with the dependent variable being the bike commuters per 10,000 population. AS well as a Binary Logit Proportional model "with the share of bike commuters in each city as the dependent variable". This paper analyzed the role of cycling infrastructure on commutership by bike in 90 of the largest 100 U.S. cities. The OLS model is used for estimating coefficients of linear regression that describe the relationship between one or more quantitative independent variables and a dependent variable. With p explanatory variables, the OLS regression model is: 
\[Y = \beta_{0}+\sum_{j=1,\dots, p}{\beta_{j}X_{j}}+\epsilon\]

\subsection{Zero-inflated Poisson regression mode}
\label{sec:pois}

paper 8, 9

@@

paper 6

>>>>

The binary logistic regression model is also used in this field of statistical research to predict the likelihood of a successful event occurring, like a high number of cycling routes close to green areas \cite{5CamposSnchez2019}. In order to conduct this model, all the variables had to be recoded to dichotomous categorical variables (1-0). For example, bicycle racks where 1=bicycle racks in buffer area, 0= no bicycle racks.

@@

The paper from \citet{3Teixeira2020} uses Multiple Level Logistic Regression to analyze the impact of cycling in various cities with different cycling infrastructure on stress markers. This analysis resulted in the data shown in Table ~\ref{fig:stress}.
\begin{figure}[tbp]
    \centering
    \includegraphics[width=0.5\textwidth]{stresstable2.jpeg}
    \caption{Distribution of Stress by City from Teixeira Study}
    \label{fig:stress}
\end{figure}

Two types of models were used in \citet{4Buehler2011}, a log-log Ordinary Least Square (OLS) model "with the dependent variable being the bike commuters per 10,000 population. As well as a Binary Logit Proportional model "with the share of bike commuters in each city as the dependent variable". This paper analyzed the role of cycling infrastructure on commutership by bike in 90 of the largest 100 U.S. cities. The OLS model is used for estimating coefficients of linear regression that describe the relationship between one or more quantitative independent variables and a dependent variable \cite{XLSTAT2023}. With p explanatory variables, the OLS regression model is: 
\[Y = \beta_{0}+\sum_{j=1,\dots, p}{\beta_{j}X_{j}}+\epsilon\]

In the group of papers selected, the multinomial logit (MNL) model was used to estimate the travel choice of bicycle for commuting \cite{10Zhao2013}.

\subsection{Zero-inflated Poisson Regression Mode}
\label{sec:pois}

A different approach that was used in the research into bike lanes was to use a zero-inflated Poisson regression model to estimate the change in cycle-motor vehicle collisions \cite{8Bhatia2016}. This model is used since the design is looking at collision rates pre to post instillation of bike lanes, and since the model allows for an over-abundance of zero counts in the data. The Poisson distribution's p.m.f is:
\[P(Y=y) = \exp{(-\lambda)\lambda^{y}}/y!\]

The Poisson model is also used in \citet{9Cantisani2021} to "address the randomness due to the perception and decision of road users at the intersections", as their research is specifically on the crash likelihood of cyclists at roundabouts with different infrastructure types.

@@

The final method identified from the surveyed papers was to use the generalized linear model to predict the vehicle delays caused by bicycle traffic versus other variables. Alongside this method, the cumulative curve method as used to extract traffic flow data from videos \cite{6Pu2017}. The basic model of the generalized linear model is:
\[Y_{nx1} = X_{nxp}\beta_{px1}+\epsilon_{nx1}\]
Where the matrix of observed values of dependent variables is  $Y_{nx1}$, $X_{nxp}$ is the matrix of observed explanatory variables, $\beta_{px1} =$ is the matrix of coefficients for explanatory variables, and $\epsilon_{nx1}$ is the error. Using this model is reported to help to understand how each factor contributed to the delay of cyclists on urban streets.
